The {\em Diff} MILP model and PCA for \\ {\em real-time} DNN robustness certification

### 2025-12-08 CAV 2026/global.tex
one line
alpha

Different bounds were proposed in \cite{vhagar}, for an evaluation purpose (how narrow is the gap between the upper and lower bound) rather than to verify images in real-time.

TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS 
$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
$\beta^{\text{perturb}}_{C,D}$ is.

>>>>

Different bounds were proposed in \cite{vhagar}, for an evaluation purpose (how narrow is the gap between the upper and lower bound) rather than to verify images in real-time. Namely, Vhagar defines $\alpha^{\text{perturb}}_{C,D}$, computing the perturbation necessary to switch an image classified as $C$ into an image classified as $D$:
\begin{align*}
	\alpha^{\text{perturb}}_{C,D} &= \max_{|I-I'| \leq \text{perturb}} (x_C-\max_{E\neq C}x_E) &\text{s.t. }  x'_D \geq \max_{E\neq D}x'_E \wedge x_C \geq \max_{E\neq C}x_E 
\end{align*}

Notice that  
$\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
$\beta^{\text{perturb}}_{C,D}$ is.
